Report: Complex Support Vector Detector for Large MIMO System

### 2015-10-14 Report Aug 5 2015/Report Aug 2015.tex
Report for CSVR revised

%\hfill September 17, 2014
  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment. The most promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} long-term evolution (LTE)\cite{3GLTE}.  The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve bandwidth efficiency) and diversity gain (better reliability of communication link) is obtained by exploiting the spatial domain. Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously. This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness both to unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.

  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving end. The uplink Detector is one of the key components in large MIMO systems. With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems. On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexity of the algorithm becomes crucial to make the system practical.

Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams. However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with number of transmitted antennas, which is prohibitive for practical applications.

@@

Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD. However, SD has two major shortages that make it problematic to be integrated into a practical systems. The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware. The second shortage is SD's complexity still has a lower bound for complexity that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different value of SNR. The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution. The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC(sel-MMSE-OSIC)\cite{radji2009interference}. However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}. Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.

%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. 
Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance. such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
Tabu search based algorithms which have superior performance compared to LAS detectors because local minima can be avoided (e.g. Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g. Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g. Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) and Lattice Reduction (LR) aided algorithms\cite{zhou2013element}.

@@

Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
Moreover, the kernel based methods\cite{scholkopf2002learning} solve nonlinear learning tasks by mapping input data sets into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space. This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS). 
Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.

Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual optimization problem, which can be solved by Quadratic Programming (QP). Sequential Minimal Optimization (SMO) algorithm was proposed as a fast algorithm to solve this QP problem by decomposing the it into sub QP problems and solving them analytically\cite{platt1999fast}. Therefore, the computational intensive numerical method can be avoided. A more general method is decomposition solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets W and N, W is the work set and N contains the remaining optimization variables. In each iteration, only the optimization variables in the work set is optimized while keeping other variables fixed. The SMO algorithm is an extreme case of decomposition solver. An important issue of decomposition solver is the choice of the work set. One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring final converge\cite{osuna1997improved}. Because of the linear constraint inducted by offset, the SMO algorithm restricts the size of the work set to 2. In\cite{steinwart2011training}, a method to train SVM without offset was proposed, with the comparable performance to the SVM with offset. A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed. The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time. The authors demonstrate that with the combination of two proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.

The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets. In communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain. The results in\cite{bouboulis2013complex} demonstrate better performances as well as reduced complexity comparing to simply split learning task into two real case by real kernel.  
Based on this work, we derive of a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR). The detector can work in two parallel real SVR channels which can be solved independently. Moreover, only the real part of kernel matrix is needed in both channels. This means a large amount of computation can be reduced.
Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed. By this strategy, two variables can be updated at each iteration, with much smaller searching time.

@@

\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
\subsection{Regression Model}
Suppose we are given training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$. $y_{i}$ denotes output. Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Lambda}$, $\Lambda \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$). The regression model (either linear or non-linear) is given by 
\begin{equation}
y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1\cdots L 
\label{equation1}
\end{equation}

@@

We present the primal optimization problem directly
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
s.t. \left\{\begin{array}{ll}
y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
\end{array}\right.
\label{primal optimization problem}
\end{IEEEeqnarray}
In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the area between two dash line is called $\epsilon$ tube. Only those data samples located outside $\epsilon$ tube contribute to cost. Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with noise of input data samples, $R(u)$ denotes risk function, the simplest risk function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}. For example if the noise is Gaussian noise, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$. The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.

@@

Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}$ are defined as  

@@

\xi_{i}=\max(0, \mathbf{y}_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\

@@

\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-\mathbf{y}_{i}-\epsilon)

@@

Because the distance of the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero. That is $\xi_{i}\hat{\xi}_{i}=0$.

@@

\sum_{i=1}^{L}log(Pr(y_{i}-f(\mathbf{x}_{i}))),

@@

maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}log(Pr(y_{i}-f(\mathbf{x}_{i})))$

@@

c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-log(P(y_{i}-f(\mathbf{x}_{i}))).

@@

Thus (\ref{cost function1}) can be rewritten as 

@@

\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),

@@

\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))

@@

the cost function term is determined according to noise distribution.  

@@

According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier. The Lagrange function is given by. 

@@

The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions. Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.

@@

L(\mathbf{w}, a_{i})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),

@@

where $a_{i}$ denote Lagrange multipliers.
 Based on Theorem 6.21 in \cite{scholkopf2002learning}, For a variable set $[\bar{\mathbf{w}}, \bar{a}_{i}]$, $\bar{\mathbf{w}}$ is the solution to (\ref{constraint optimization problem}) only when the following inequalities are satisfied

@@

 L(\mathbf{w}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, \bar{a}_{i})\geq L(\bar{\mathbf{w}}, a_{i})

@@

This inequalities yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 

@@

\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, a_{i})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\

@@

\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{a}_{i})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\

@@

\frac{\partial L}{\partial \mathbf{w}}=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\

@@

\frac{\partial L}{\partial \xi_{i}}=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\

@@

\frac{\partial L}{\partial \hat{\xi}_{i}}=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\

@@

\frac{\partial L}{\partial b}=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber

@@

+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}(y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i})+\\
\sum_{i=1}^{L}\hat{\alpha}_{i}(\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i})

@@

+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]\\
s.t.\left\{\begin{array}{l}
\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha_{i}})=0\\
0<\alpha<C\tilde{R}^{'}(\alpha)\\
0<\hat{\alpha}<C\tilde{R}^{'}(\hat{\alpha})\\

@@

In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold. Condition (\ref{original KKT condition2}) is satisfied when the maximum of $L(\bar{\mathbf{w}}, a_{i})$ is found, notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\bar{\mathbf{w}}, a_{i})$ in (\ref{KKT inequalities}), thus yielding the dual optimization problem, which is given by 

@@

based on (\ref{gain work set selection lambda}), The maximal gain of objective function with respect to the $m$th optimization variable $\lambda_{m}$ is 

@@

\Phi^{r}=Re(\mathbf{y})-\mathbf{K}^{r}

>>>>

%\hfill September 17, 2014
  One of the biggest challenges the researchers and industry practitioners are facing in wireless communication area is how to bridge the sharp gap between increasing demand of high speed communication of rich multimedia information with high level Quality of Service (QoS) requirements and the limited radio frequency spectrum over a complex space-time varying environment. The promising technology for solving this problem, Multiple Input Multiple Output (MIMO) technology has been of immense research interest over the last several tens of years is incorporated into the emerging wireless broadband standard like 802.11ac\cite{IEEE802.11ac} and long-term evolution (LTE)\cite{3GLTE}.  The core idea of MIMO system is to use multiple antennas at both transmitting and receiving end, so that multiplexing gain (multiple parallel spatial data pipelines that can improve spectrum efficiency) and diversity gain (better reliability of communication link) are obtained by exploiting the spatial domain. Large MIMO (also called Massive MIMO) is an upgraded version of conventional MIMO technology employing hundreds of low power low price antennas at base station (BS), that serves several tens of terminals simultaneously. This technology can achieve full potential of conventional MIMO system while providing additional power efficiency as well as system robustness to both unintended man-made interference and intentional jamming.\cite{rusek2013scaling}\cite{larsson2014massive}.

  The price paid for large MIMO system is the increased complexities for signal processing at both transmitting and receiving ends. The uplink detector is one of the key components in a large MIMO system. With orders magnitude more antennas at the BS, benefits and challenges coexist in designing of detection algorithms for the uplink communication of large MIMO systems. On one hand, a large number of receive antennas provide potential of large diversity gains, on the other hand, complexities of the algorithms become crucial to make the system practical.

Vertical Bell Laboratories Layered Space-Time (V-BLAST) architecture for MIMO system can achieve high spectrum efficiency by spatial multiplexing (SM), that is, each transmit antenna transmits independent symbol streams. However the optimal maximum likelihood detector (MLD) for V-BLAST systems that perform exhaustive search has a complexity that increases exponentially with the number of transmitted antennas, which is prohibitive for practical applications.

@@

Sphere Decoder (SD)\cite{damen2003maximum} is the most prominent algorithm that utilizes the lattice structure of MIMO systems, which can achieve optimal performance with relatively much lower complexity comparing to MLD. However, SD has two major shortages that make it problematic to be integrated into a practical systems. The first shortage is SD has various complexities under different signal to noise ratios (SNR), while a constant processing data rate is required for hardware. The second shortage is the complexity of SD still has a lower bound that increases exponentially with the number of transmit antennas and the order of modulation scheme\cite{jalden2005complexity}.
The fixed complexity sphere decoder (FCSD)\cite{barbero2008fixing} makes it possible to achieve near optimal performance with a fixed complexity under different values of SNR. The FCSD inherits the principle of list based searching algorithms, which first generate a list of candidate symbol vectors and then the best candidate is chosen as the solution. The other sub optimal detectors belong to this class include Generalized Parallel Interference Cancellation (GPIC)\cite{luo2008generalized} and Selection based MMSE-OSIC (sel-MMSE-OSIC)\cite{radji2009interference}. However, all these list based searching algorithms have the same shortage - their complexities increase exponentially with the number of transmit antennas and the order of modulation scheme\cite{radji2009interference}. Therefore, such algorithms are prohibitive when it comes to a large number of antennas or a high order modulation scheme, for example in IEEE 802.11ac standard\cite{IEEE802.11ac}, the modulation scheme is 256QAM.

%Linear detectors (LD) like minimum mean square error (MMSE) and zero forcing (ZF) along with their sequential interference cancellation with optimized ordering (OSIC) counterparts\cite{wolniansky1998v}, which have good performance for low loading factor in massive MIMO system (the number of receive antennas is much larger than the number of transmit antennas)\cite{hoydis2013massive}. 
Besides the above detection algorithms designed for conventional MIMO systems, in the last several years, a set of metaheuristic based detection algorithms have been proposed for large MIMO systems with complexities that are comparable with MMSE detector and near-optimal performance. such algorithms include likelihood ascend searching (LAS) algorithms\cite{vardhan2008low}\cite{li2010multiple}, %An theoretical analysis of upper bound of bit error rate (BER) and lower bound of on asymptotic multiuser efficiency for the LAS detector was also presented\cite{sunfamily}.
Tabu search based algorithms which have superior performances compared to LAS detectors because of the efficient local minima exit strategy (e.g. Layered Tabu search (LTS)\cite{srinidhi2011layered}, Random Restart Reactive Tabu search (R3TS)\cite{datta2010random}), Message passing technique based algorithms (e.g. Belief propagation (BP) detectors based on graphic model and Gaussian Approximation (GA)\cite{som2011low}\cite{som2010improved}\cite{narasimhan2014channel}\cite{goldberger2011mimo}), Probabilistic Data Association based algorithms \cite{mohammed2009low}, Monte Carlo sampling based algorithms (e.g. Markov Chain Monte Carlo (MCMC) algorithm\cite{datta2013novel}) . Moreover, element based Lattice Reduction (LR) aided algorithms were also proposed to  large MIMO systems.\cite{zhou2013element}.

@@

Interest in SVM boosted since 1990s, promoted by the works of Vapnik and co-workers at AT\& T Bell laboratory\cite{boser1992training}\cite{guyon1993automatic}\cite{vapnik2013nature}\cite{cortes1995support}\cite{scholkopf1996incorporating}\cite{vapnik1996support}.
Moreover, the kernel based methods\cite{scholkopf2002learning} were proposed which solve nonlinear learning tasks by mapping input data samples into high dimensional feature spaces, and replacing inner products of feature mappings by computational inexpensive kernel functions discarding the actual structure of the feature space. This rationale is supported mathematically by the notion of Reproducing Kernel Hilbert Space (RKHS). 
Based on the same regularized risk function principle, $\epsilon$-Support Vector Regression ($\epsilon$-SVR) was developed\cite{vapnik2013nature}\cite{smola2004tutorial}.

Similar to SVM, the $\epsilon$-SVR solves an original optimization problem by transforming it into a Lagrange dual form, which can be solved by Quadratic Programming (QP). Decomposition methods were proposed to solve this QP problem by decomposing it into sub QP problems and solving them iteratively\cite{platt1999fast}. Therefore, the computational intensive numerical methods can be avoided. Decomposition is performed by sub set selection solver, which refers to a set of algorithms that separate the optimization variables (Lagrange multipliers) into two sets S and N, S is the work set and N contains the remaining optimization variables. In each iteration, only the optimization variables in the work set is updated while keeping other optimization variables fixed. The Sequential Minimal Optimization (SMO) algorithm\cite{platt1999fast} is an extreme case of the decomposition solvers. An important issue of the sub set selection solvers is the selection of the work set. One strategy is to choose Karush-Kuhn-Tucker (KKT) condition violators, ensuring the final converge\cite{osuna1997improved}. The SMO algorithm restricts the size of the work set to two. A method to train SVM without offset was proposed In\cite{steinwart2011training}, with the comparable performance to the SVM with offset. A set of sequential single variable work set selection strategies, which require $O(n)$ searching time are proposed. The optimal double variable work set selection strategy, which performs exhaustively searching, however, requires $O(n^{2})$ searching time. The authors demonstrate that with the combination of two different proposed single variable work set selection strategies, convergence can be achieved by a iteration time that is as few as optimal double variable work set selection strategy.

The mathematical foundation of kernel based methods is RKHS which is defined in complex domain, however most of the practitioners are dealing with real data sets. In communication and signal processing area, the channel gains, signals, waveforms etc. are all represented in complex form. Recently, a pure complex SVR \& SVM based on complex kernel was proposed in\cite{bouboulis2013complex}, which can deal with the complex data set purely in complex domain. The results in\cite{bouboulis2013complex} demonstrate the better performance as well as reduced complexity comparing to simply split learning task into two real case by real kernels.  
Based on this work, we derive a complexity-performance controllable detector for large MIMO systems based on a dual channel complex SVR (CSVR). The detector can work in two parallel real SVR channels which can be solved independently. Moreover, only the real part of kernel matrix is needed in both channels. This means a large amount of computation cost saving can be achieved.
Based on the discrete time MIMO channel model, in our regression model, this CSVR-detector
is constructed without offset, Therefore, for each real SVR without offset, 
%in principle, only one variable is needed to be updated in each iteration, In our scheme, a sequential single variable selection strategy is proposed. By this strategy, two variables can be updated at each iteration, with much smaller searching time.
Two types of combined single optimization variable selection strategy are proposed based on the work in \cite{steinwart2011training}. The proposed combined single optimization variable selection strategy can approximate optimal double optimization variable selection strategy. The former one can achieve as few as iteration time while enjoy significant speed gain in each iteration.

@@

\section{Brief Introduction to $\epsilon$-Support Vector Regression}\label{Introduce epsilon SVR}
\subsection{Regression Model}
Suppose we are given a training data set $((\mathbf{x}_{1}, y_{1}),(\mathbf{x}_{2},y_{2}),\cdots,(\mathbf{x}_{L},y_{L}))$, $L$ denotes the number of training samples, $\mathbf{x}_{i}\in \mathbb{R}^{V}$ denotes input data vector, $V$ is the number of features in $\mathbf{x}_{i}$. $y_{i}$ denotes output. Let $\mathbf{w}$ denotes regression coefficient vector, $\Phi(\mathbf{x}_{i})$ denotes the mapping of $\mathbf{x}_{i}$ to higher dimensional feature space, $\mathbf{w},\Phi(\mathbf{x}_{i})\in \mathbb{R}^{\Omega}$, $\Omega \in \mathbb{R}$ denotes the dimension of mapped feature space (For linear model, $\mathbf{x}_{i}=\Phi(\mathbf{x}_{i})$, $\Omega=V$). The regression model (either linear or non-linear) is given by 
\begin{equation}
y_{i}=\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b  \quad i= 1,2,\ldots, L
\label{equation1}
\end{equation}

@@

We present the primal optimization problem directly
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
\min_{\mathbf{w}} f(\mathbf{w})=\frac{1}{2}||\mathbf{w}||^{2}+C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))\\
s.t. \left\{\begin{array}{ll}
y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b \leq \epsilon+\xi_{i}, i=1,2\cdots, L \\
\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i} \leq \epsilon+\hat{\xi}_{i}, i=1,2\cdots, L\\
\epsilon_{i}, \xi_{i},\hat{\xi}_{i} \geq 0, i=1,2\cdots, L
\end{array}\right.
\label{primal optimization problem}
\end{IEEEeqnarray}
In (\ref{primal optimization problem}), $\frac{1}{2}||\mathbf{w}||^{2}$ is the regularization term in order to ensure the flatness of regression model, $\epsilon$ denotes the precision, As shown in Fig \ref{epsilon-SVR}, the solid line represents the estimation of the input-output relation, the area between two dash lines ($\epsilon$-bound) is called $\epsilon$-tube. Only those data samples located outside $\epsilon$-tube contribute to the estimation error. Furthermore $\xi_{i}$ and $\hat{\xi}_{i}$ denote slack variables that cope with additive noise of observations, $R(u)$ denotes the cost function. The simplest cost function is $R(u)=u$, The type of cost function is determined by the statistical distribution of noise\cite{smola2004tutorial}. For example if the noise is Gaussian distributed, then the optimal cost function is $R(u)=\frac{1}{2}u^{2}$. The term $C\sum_{i=1}^{L}(R(\xi_{i})+R(\hat{\xi}_{i}))$ denotes the penalty of noise, $C\in \mathbb{R}$ and $C\geq 0$ that controls the trade off between regularization term and cost function term.

@@

Therefore in $\epsilon$-SVR, $\xi_{i}$ and $\hat{\xi}_{i}$ are defined as  

@@

\xi_{i}=\max(0, y_{i}-\mathbf{w}^{T}\Phi(\mathbf{x}_{i})-b-\epsilon)\\

@@

\hat{\xi}_{i}=\max(0, \mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon).

@@

Because the distance between the estimations $\mathbf{w}^{T}\Phi(\mathbf{x}_{i})+b$ and the observation $\mathbf{y}_{i}$ can only exceeds the $\epsilon$-tube in one direction, therefore there is at most one of $\xi_{i}$ and $\hat{\xi}_{i}$ can be non zero. That is $\xi_{i}\hat{\xi}_{i}=0$.

@@

\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),

@@

maximizing (\ref{cost function2}) is equivalent to minimizing $-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i})))$, therefore (\ref{cost function1}) is equivalent to 
\min_{f}-\sum_{i=1}^{L}\log(Pr(y_{i}-f(\mathbf{x}_{i}))),

@@

c(\mathbf{x}_{i}, y_{i}, f(\mathbf{x}_{i}))=-\log(P(y_{i}-f(\mathbf{x}_{i}))).

@@

Thus (\ref{cost function3}) can be rewritten as 

@@

\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon})),

@@

\sum_{i=1}^{L}R(\xi_{i})+R(\hat{\xi}_{i})=\sum_{i=1}^{L}\tilde{c}(y_{i}, \mathbf{x}_{i}, f(\mathbf{x}_{i}))=\sum_{i=1}^{L}-\log(Pr(|y_{i}-f(\mathbf{x}_{i})|_{\epsilon}))

@@

the cost function term is determined according to the distribution of noise.  

@@

According to Lagrange Theorem, the constraint optimization problem (\ref{primal optimization problem}) can be transformed to Lagrangian dual form by combining the original optimization function with inequality constraints, the combination coefficient is called Lagrange multiplier. The Lagrange function is given by 

@@

The sufficient and necessary conditions such that a solution $\mathbf{w}$ of the primal constrained optimization problem in (\ref{primal optimization problem}) satisfies, are called Karush-Kuhn-Tucker (KKT) conditions. Here we elaborate a little further about how the dual objective problem is derived from KKT conditions.

@@

L(\mathbf{w}, \mathbf{a})=f(\mathbf{w})+\sum_{i=1}^{L}a_{i}c_{i}(\mathbf{w}),

@@

where $\mathbf{a}=[a_{1},a_{2},\ldots, a_{L}]^{T}$ denotes the vector consist of Lagrange multipliers.
 Based on Theorem 6.21 in \cite{scholkopf2002learning}, a variable pair $[\bar{\mathbf{w}}, \bar{\mathbf{a}}]$ is the solution to (\ref{constraint optimization problem}) if and only if the following inequalities are satisfied

@@

 L(\mathbf{w}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \bar{\mathbf{a}})\geq L(\bar{\mathbf{w}}, \mathbf{a})

@@

This inequalities (also called saddle point conditions) yield KKT conditions (see Theorem 6.26 \cite{scholkopf2002learning}), which are 

@@

\partial_{\mathbf{w}}L(\bar{\mathbf{w}}, \mathbf{a})=\partial_{\mathbf{w}}f(\bar{\mathbf{w}})+\sum_{i=1}^{L}a_{i}\partial_{\mathbf{w}}c_{i}(\bar{\mathbf{w}})=0,\\

@@

\partial_{a_{i}}L(\bar{\mathbf{w}}, \bar{\mathbf{a}})=c_{i}(\bar{\mathbf{w}})\leq 0, i=1,2,\ldots L\\

@@

\partial_{\mathbf{w}} L=\mathbf{w}-\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})\Phi(\mathbf{x}_{i})=0\\

@@

\partial_{\xi_{i}}L=C_{i}R^{'}(\xi_{i})-\eta_{i}-\alpha_{i}=0, i=1,2,\cdots L\\

@@

\partial_{\hat{\xi}_{i}}L=C_{i}R^{'}(\hat{\xi_{i}})-\hat{\eta}_{i}-\hat{\alpha}_{i}=0, i=1,2,\cdots L\\

@@

\partial_{b}L=\sum_{i=1}^{l}(\alpha_{i}-\hat{\alpha}_{i})=0\\\nonumber

@@

+(CR^{'}(\hat{\xi}_{i})-\hat{\alpha}_{i})\hat{\xi}_{i}]+\sum_{i=1}^{L}\alpha_{i}[y_{i}-\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})-b-\epsilon-\xi_{i}]+\\
\sum_{i=1}^{L}\hat{\alpha}_{i}[\sum_{j=1}^{L}(\alpha_{j}-\hat{\alpha}_{j})\Phi^{T}(\mathbf{x}_{j})\Phi(\mathbf{x}_{i})+b-y_{i}-\epsilon-\hat{\xi}_{i}]

@@

+\sum_{i=1}^{L}[(\alpha_{i}-\hat{\alpha_{i}})y_{i}-(\alpha_{i}+\hat{\alpha_{i}})\epsilon]

@@

In order to satisfy the second inequality in (\ref{KKT inequalities}), (\ref{original KKT condition2}) and  (\ref{original KKT condition3}) have to hold. A $\mathbf{w}$ that satisfies the conditions in (\ref{original KKT condition2}) is in the feasible region defined by inequality constraints as mentioned (\ref{constraint optimization problem}). In $\epsilon$-SVR, this condition is satisfied by making use of the slack variables $\xi_{i}$ and $\hat{\xi}_{i}$ defined in (\ref{definition of slack variable1}) and (\ref{definition of slack variable2}). Define that $\tilde{\mathbf{w}}$ is in the feasible region and satisfies the conditions in (\ref{original KKT condition1}), notice $\theta(\alpha_{i}, \hat{\alpha}_{i})$ is equivalent to $L(\tilde{\mathbf{w}}, \mathbf{a})$, thus yielding the dual optimization problem, which is given by 

@@

based on (\ref{gain work set selection lambda}), The maximal gain of the sub dual objective function with respect to the $m$th optimization variable is 

@@

\Phi^{r}=\Re(\mathbf{y})-\Re(\mathbf{K})
